JavaScript as an Embedded DSL

### 2012-03-30 papers/ecoop2012/article.tex
Added footnote to functions reification equeation.

It's important to note that reification preserves function composition. Specifically, let \code{f: Rep[A] => Rep[B]} and \code{g: Rep[B] => Rep[C]} then {\tt\small fun(g compose f) == (fun(g) compose fun(f))} where we consider two reified functions to be equal if they yield the same observable effects at runtime. That property of function reification is at the core of reusing the continuation monad in our DSL. Thanks to the fact that the continuation monad composes functions, we can just insert reification at some places (like in a \code{sleep}) and make sure that we reify \emph{effects} of the continuation monad without the need to reify the monad itself.

>>>>

It's important to note that reification preserves function composition (roughly speaking it's homomorphism between DSL code and generated JavaScript code).
Specifically, let \code{f: Rep[A] => Rep[B]} and \code{g: Rep[B] => Rep[C]} then {\tt\small fun(g compose f) == (fun(g) compose fun(f))}
where we consider two reified functions to be equal if they yield the same observable effects at runtime
\footnote{Note that composition on the left and the right hand side of the equation is not the same operation but they have the same observable runtime effect.}.
That property of function reification is at the core of reusing the continuation monad in our DSL. Thanks to the fact that the continuation monad composes functions, we can just insert reification at some places (like in a \code{sleep}) and make sure that we reify \emph{effects} of the continuation monad without the need to reify the monad itself.
